\section{Time box 2}
\subsection{Time box planning}
Show meeting in week 11.
\subsubsection{Work to be done in this time box}
\begin{itemize}
	\item ARM to FPGA interface
	\begin{itemize}
		\item Mount
		\item Test
	\end{itemize}
	\item PLC module
	\begin{itemize}
		\item Mount x7
		\item Test
	\end{itemize}
	\item Daemon
	\item Power switch
	\begin{itemize}
		\item Block diagram
	\end{itemize}
	\item Host controller
	\item Master wishbone
\end{itemize}
\paragraph{Description:}
\begin{description}
	\item[ARM to FPGA interface] The connection between the ARM7 CPU and the FPGA board, has to be mounted, tested and debugged.
	\item[PLC module] The powerline module has to be mounted 7 times for all the groups, tested and debugged.
	\item[Daemon] 
	\item[Power switch] Block diagram of the power switch, which shall activate the different modules connected to it (wind-turbine, photo-voltaic cells etc.) and control the current flow.
	\item[Host controller] The host controller is the block in the FPGA that control the input form the ARM7 CPU. This block has to be design as an IP core with wishbone interface.
	\item[Master wishbone] The wishbone interface for the host controller has to be made as master to control the FPGA blocks.
\end{description}

\subsection{ARM to FPGA interface}



\subsection{PLC module}



\subsection{Daemon}



\subsection{Power switch}
The power switch is the part of the hub that traffics the current from and to its connected modules. 
\\ Inspiration: 
\url{http://www.pwrhub.com/}
\\ \url{http://www.linear.com/product/LTC4357}
\\ \url{http://cds.linear.com/docs/Demo\%20Board\%20Manual/dc1203A.pdf} demo board.
\\ Power Mosfets:
\url{http://pdf1.alldatasheet.com/datasheet-pdf/view/234175/IRF/IRFP4468PBF.html}
\\ Power rectifiers
\url{http://pdf1.alldatasheet.com/datasheet-pdf/view/172142/ONSEMI/MBR60H100CT.html}


\subsection{Host controller}



\subsection{Master wishbone}

