\chapter{Realisation Phase}
The realisation phase, is where all the analysis, design, implementation, verification and deployments is made. This phase is divided into several timeboxes, where small parts of the development is done in steps. A timebox is a 2 week time period where parts of the product is made ready for deployments for the end product.
\p The work that shall be done to complete the project is stated below:\p
\textbf{System setup / Design:}\cite{greenwade93}\\
CO/Module-design. Deadline in week 10\\
Relay server. Deadline tuesday week 9\\
Daemon. Deadline week 11\\
Almost complete system. Deadline week 13\\
Complete system. Deadline week 15\\
\\
\textbf{Hardware:}\\
\textit{ARM7 / FPGA connector}\\
- Schematic\\
- Print layout\\
- Mounting\p
\textit{PLC module + 5v supply (Dennis responsible with Kristian). Deadline week 9}\\
- Schematic\\
- Print layout\\
- Mounting\\
- Functional test\\
- EMC test\p
\textit{Power switch:}\\
	- Block diagram with state machine\\
	- Schematic\\
	- Simulation\\
	- Print layout\\
	- Mounting\\
	- Testing\p
\textit{FPGA extension board}\\
- Schematic (Temp + humidity circuit + current sensor circuit)\\
- Print layout\\
- Mounting\\
- Functional test\p
\textit{Converters}\\
- 230VAC - 30VDC inverter\\
- 30VDC - 230VAC converter\\
- Possible Variable load.\\\p
\textbf{Mechanic:}\\
Box for the hub\p
\textbf{Software:}\\
Web application - Database and server side programming\\
ADC\\
Daemons\\
Drivers\\

%\section{Project time plan}
\input{content/realisation/tb1.tex}\newpage
\input{content/realisation/tb2.tex}\newpage
%\input{content/realisation/tb3.tex}\newpage
%\input{content/realisation/tb4.tex}\newpage
%\input{content/realisation/tb5.tex}\newpage
%\input{content/realisation/tb6.tex}\newpage
%\input{content/realisation/tb7.tex}\newpage
%\input{content/realisation/tb_next.tex}